GEE models

### 2017-07-11 doc/esm-figures.Rmd
updated esm figure file with dagitty images

sfig_consort <- sfig('consort', 'CONSORT diagram of sample size at each examination visit.')
sfig_dag <- sfig("dagitty", "Directed acyclic graph taken from DAGitty (DAGitty.net).")
sfig_corr_conc <- sfig('corr_conc', 'Pearson correlation heatmap of non-esterified fatty acids (*nmol/mL*) and basic PROMISE participant characteristics for the baseline visit (2004-2006). Darkness of the colour indicates the magnitude of the correlation, with orange indicating positive and blue indicating negative correlations.')
sfig_corr_pct <- sfig('corr_pct', 'Pearson correlation heatmap of non-esterified fatty acids (*mol%*) and basic PROMISE participant characteristics for the baseline visit (2004-2006). Darkness of the colour indicates the magnitude of the correlation, with orange indicating positive and blue indicating negative correlations.')
```

@@

![`r sfig_dag`](../img/dagitty.png)

>>>>

sfig_consort <- sfig('consort', 'CONSORT diagram of sample size at each examination visit.')
sfig_dag_isi <- sfig("dag_isi", "Directed acyclic graph taken from DAGitty (DAGitty.net) for the potential causal pathway between NEFA and ISI.")
sfig_dag_issi2 <- sfig("dag_issi2", "Directed acyclic graph taken from DAGitty (DAGitty.net) for the potential causal pathway between NEFA and ISSI-2.")
sfig_corr_conc <- sfig('corr_conc', 'Pearson correlation heatmap of non-esterified fatty acids (*nmol/mL*) and basic PROMISE participant characteristics for the baseline visit (2004-2006). Darkness of the colour indicates the magnitude of the correlation, with orange indicating positive and blue indicating negative correlations.')
sfig_corr_pct <- sfig('corr_pct', 'Pearson correlation heatmap of non-esterified fatty acids (*mol%*) and basic PROMISE participant characteristics for the baseline visit (2004-2006). Darkness of the colour indicates the magnitude of the correlation, with orange indicating positive and blue indicating negative correlations.')
```

@@

![`r sfig_dag_isi`](../img/dagitty-isi.png)

![`r sfig_dag_issi2`](../img/dagitty-issi2.png)
